### 2021-05-09 papers/SYRCoSE/future.tex
Use xspace to handle spaces after \newcommands such as \coq

Finally, we plan to mechanise in Coq classical results 
that connect various classes of event structures%  
~\cite{Nielsen-al:1981, Boudol-Castellani:1991}. 
It would allow us to easily establish the connection between operational and denotational 
semantics of concurrent languages.

>>>>

Finally, we plan to mechanise in \coq classical results 
that connect various classes of event structures%  
~\cite{Nielsen-al:1981, Boudol-Castellani:1991}. 
It would allow us to easily establish the connection between operational and denotational 
semantics of concurrent languages.

### 2021-05-09 papers/SYRCoSE/intro.tex
Use xspace to handle spaces after \newcommands such as \coq

The same information can be encoded in a single 
event structure containing $6$ events in total
(see \cref{fig:intro-es}). 
In the event structure there are two types of edges 
between the events. The grey arrows $e_1 \arrowCA e_2$ 
represent the \emph{causality relation}, a 
partial order reflecting the causal relationship
between the atomic events of computation.
The red edges $e_1 \arrowCF e_2$ represent 
the \emph{conflict relation} which is 
a symmetric and irreflexive relation 
encoding mutually exclusive events.
Each particular trace can be extracted from the event structure
as a linearisation of some \emph{configuration}, 
that is a causally-closed and conflict-free 
subset of events.

@@

The programming languages theory and formal semantics research communities 
are moving to increase the usage of \emph{proof assistants} 
like Coq, Agda, Isabelle, Arend, and others,
to complement theoretical studies with their mechanisation,
as this process increases the reliability and reproducibility 
of scientific results.
Yet, to the best of our knowledge, there is little work on 
mechanisation of the theory of event structures.
The present report aims to close the gap.

Our goal is to develop a Coq library containing 
a comprehensive set of common definitions, lemmas, 
and tactics that would allow researchers 
to utilise the theory of event structures 
for the needs of their domain.

>>>>

The same information can be encoded in a single 
event structure containing $6$ events in total
(see \cref{fig:intro-es}). 
In the event structure there are two types of edges 
between the events. The grey arrows $e_1 \arrowCA e_2$ 
represent the \emph{causality relation}, a 
partial order reflecting the causal relationship
between the atomic events of computation.
The red edges $e_1 \arrowCF e_2$ represent 
the \emph{conflict relation} which is 
a symmetric and irreflexive relation 
encoding mutually exclusive events.
Each particular trace can be extracted from the event structure
as a linearisation of some \emph{configuration}, 
that is a causally-closed and conflict-free subset of events,  
which additionally should satisfy the constraint 
that each read is preceded by a matching write.

@@

The programming languages theory and formal semantics research communities 
are moving to increase the usage of \emph{proof assistants} 
like \coq~\cite{Coq}, \agda~\cite{Agda}, 
\isabelle~\cite{Nipkow-al:Isabelle2002}, 
\arend~\cite{Arend}, and others,
to complement theoretical studies with their mechanisation,
as this process increases the reliability and reproducibility 
of scientific results.
Yet, to the best of our knowledge, there is little work on 
mechanisation of the theory of event structures.
The present report aims to close the gap.

Our goal is to develop a \coq library containing 
a comprehensive set of common definitions, lemmas, 
and tactics that would allow researchers 
to utilise the theory of event structures 
for the needs of their domain.

### 2021-05-09 papers/SYRCoSE/overview.tex
Use xspace to handle spaces after \newcommands such as \coq

We build our mechanisation on top of the \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
using the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq~system.
We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of \ssreflect.

@@

To facilitate computable semantics, we define a subclass of
finitely supported event structures as a finite sequence of events
combined with finitely supported function which enhance events with 
additional information, such as their labels, causality predecessors, \etc 
Encoding finitely supported functions is not a trivial endeavor in
a proof assistant and for this task we use the \finmap~%
\footnote{\url{https://github.com/math-comp/finmap}}
library which is an extension of \mathcomp~providing finite sets and
finite maps on types with a choice opeartor (rather than on finite types).

Finally, to encode the algebraic hierarchy of various classes of event structures
we use yet another feature of \mathcomp~--- 
\emph{packed classes}~\cite{Garillot-al:ICTPHOL2009},
which is a design pattern providing multiple inheritance,
maximal sharing of notations and theories,
and automated structure inference. % and it also deals with performance issues.

>>>>

We build our mechanisation on top of the \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
using the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq system.
We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of \ssreflect.

@@

To facilitate computable semantics, we define a subclass of
finitely supported event structures as a finite sequence of events
combined with finitely supported function which enhance events with 
additional information, such as their labels, causality predecessors, \etc 
Encoding finitely supported functions is not a trivial endeavor in
a proof assistant and for this task we use the \finmap~%
\footnote{\url{https://github.com/math-comp/finmap}}
library which is an extension of \mathcomp providing finite sets and
finite maps on types with a choice opeartor (rather than on finite types).

Finally, to encode the algebraic hierarchy of various classes of event structures
we use yet another feature of \mathcomp --- 
\emph{packed classes}~\cite{Garillot-al:ICTPHOL2009},
which is a design pattern providing multiple inheritance,
maximal sharing of notations and theories,
and automated structure inference. % and it also deals with performance issues.
